%!TEX TS-program = xelatex

\documentclass[11pt, letterpaper]{awesome-cv}
\geometry{
	left     = 1.4cm,
	top      = 1.4cm,
	right    = 1.4cm,
	bottom   = 1.4cm,
	footskip = 0.5cm
}
\fontdir[fonts/]

% Color for highlights
\colorlet{awesome}{black}

\name{}{DANIEL MILLER}
\mobile{402.512.4475} 
\email{daniel.keegan.miller@gmail.com}
\linkedin{daniel-miller}

\begin{document}
\makecvheader





\cvsection{Summary}

\begin{cvparagraph}
Math Ph.D.~candidate about to join Microsoft's \href{http://www.exp-platform.com/Pages/default.aspx}{Analysis and Experimentation} team as a data scientist. 
Have experience developing scalable algorithms in a team environment, visualizing complex data, and communicating ideas to a diverse audience.
Have constructed sophisticated multidimensional objects and analyzed their statistical properties, and also led the creation of a lightweight, distributed, cloud-hosted website. 
Interested in leveraging mathematical skills to glean business insights from real-world data sets in a fast-paced, collaborative environment. 
\end{cvparagraph}





\cvsection{Education}

\begin{cventries}

\cventry
	{Ph.D.~in Mathematics, Cornell University}
	{}{}
	{May 2017}
	{
		\begin{cvitems}
			\item{Managed the creation of a location-centric auction site written in C\# and hosted on Azure.}
			\item{Achieved 20ms response rate at up to 2K requests per second distributed over 10 servers.}
			\item{Collaborated in writing a CPU scheduler and gossip-based networking protocol in C.}
		\end{cvitems}
	}
	
\cventry
	{M.S.~in Mathematics, Cornell University}
	{}{}
	{May 2017}
	{}
	
\cventry
	{B.S.~in Mathematics, University of Nebraska Omaha}
	{}{}
	{August 2012}
	{
		\begin{cvitems}
			\item{Minored in Computer Science, graduated \emph{summa cum laude}, GPA 4.0.}
			\item{Dean's List all semesters, Highest Honors in Mathematics, with senior thesis.}
			\item{Designed and wrote a compiler for a C-family programming language in Standard ML.}
		\end{cvitems}
	}
	
\end{cventries}





\cvsection{Research}

\begin{cventries}

\cventry
	{Ph.D.~Research, Cornell University}
	{}{}
	{August 2013--May 2017}
	{
		\begin{cvitems}
			\item{Developed and implemented new algorithms for computing statistical fitness of large data sets.}
			\item{Discovered mathematical application of previously unused techniques for numerical integration.}
			\item{Proved precise connections between apparently unconnected topics (discrepancy and Dirichlet series).}
			\item{Demonstrated computability of ``torsion classes,'' a highly abstract theoretical construct.}
		\end{cvitems}
	}
		
\cventry
	{Arizona Winter School, University of Arizona}
	{}{}
	{May 2013--2016}
	{
		\begin{cvitems}
			\item{Mastered concepts, ran simulations, and proved theorems in a high-intensity one week program.}
			\item{Collaborated with a diverse team to develop and present new mathematics quickly.}
		\end{cvitems}
	}
	
\cventry
	{Summer Mathematics Institute, Cornell University}
	{}{}
	{Summer 2011}
	{
		\begin{cvitems}
			\item{Created and visualized a high-dimensional example that disproved a conjecture.}
			\item{Coauthored \href{http://dx.doi.org/10.1016/j.topol.2011.11.041}{\emph{Strongly non-embeddable metric spaces}}. Topology Appl.~\textbf{159} (2012), no.3, 749--755.}
			\item{Coauthored \href{http://dx.doi.org/10.1016/j.jmaa.2014.01.063}{\emph{Polygonal equalities and virtual degeneracy in L\textsubscript{p} spaces}}. J.~Math.~Anal.~Appl.~\textbf{415} (2014), no.1, 247--268.}
		\end{cvitems}
	}
\end{cventries}





\cvsection{Leadership}

\begin{cvparagraph}
\textbf{Teaching Assistant}, \emph{Cornell University}. Coordinated logistics, teaching, and grading for a course with 300 students, 12 faculty, and 12 undergraduate assistants.
Assisted in teaching mathematics at undergraduate and graduate levels.

\textbf{Resident Assistant}, \emph{Chesterton House}. Directed event-planning, recruitment, and finances for an academic living center. 
\end{cvparagraph}





\cvsection{Skills}

\begin{cvparagraph}
\textbf{Programming:} C\#, R, Python, Java, ASP.NET, C, and \LaTeX.

\textbf{Web:} 
\href{https://azure.microsoft.com/}{Azure}, 
\href{https://aws.amazon.com/}{Amazon Web Services} (AWS), 
HTML, 
CSS, and 
\href{http://vsync.codeplex.com/}{Vsync}.
\end{cvparagraph}





\end{document}
