%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV

\documentclass[11pt, letterpaper]{awesome-cv}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-emerald}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\name{Daniel K.}{Miller}
\position{Mathematician{\enskip---\enskip}Data scientist}
\address{190 Pleasant Grove Road Apartment I5, Ithaca, NY 14850-2610, USA}
\mobile{(+1) 402-512-4475} 
\email{dm635@cornell.edu}
\homepage{www.math.cornell.edu/\textasciitilde dkmiller/}
\github{dkmiller}
\linkedin{dkmiller}
\mathoverflow{6856}{daniel-miller}

% Uncomment if you would like the quote to be visible.
%\quote{``The world we live in is vastly different from the world we think we live in.'' ---Nassim Taleb}

\begin{document}

% Print the header with above personal informations
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Daniel K.~Miller~~~·~~~Résumé}
  {\thepage}



\cvsection{Summary}
\begin{cvparagraph}

My current work is on the statistical properties of the Satake parameters of elliptic curves and abelian 2-folds. The Sato--Tate conjecture (now proved by Taylor et.~al.) states that the Satake parameters are equidistributed with respect to the Sato--Tate measure. Akiyama and Tanigawa made a conjecture on the precise nature of this distribution---namely a bound on the star-discrepancy of the sequence of Satake parameters. I have generalized this conjecture to arbitrary motives, and am proving a tight web of implications between variants of this conjecture and the analytic properties of a curious class of \emph{L}-functions. I am also 
developing new techniques for the fast computation of star-discrepancy with respect to measures with non-convex CFDs. 
\end{cvparagraph}





\cvsection{Education}

\begin{cventries}

\cventry
	{Ph.D.~in Mathematics}
	{Cornell University}
	{Ithaca, NY}
	{August 2012--PRESENT}
	{
		\begin{cvitems}
			\item{Won the Eleanor Norton York Award.}
		\end{cvitems}
	}
	
\cventry
	{Master's in Computer Science}
	{Cornell University}
	{Ithaca, NY}
	{August 2015--PRESENT}
	{}
	
\cventry
	{B.S.~in Mathematics}
	{University of Nebraska Omaha}
	{Omaha, NE}
	{August 2009--July 2012}
	{
		\begin{cvitems}
			\item{Minor in Computer Science.}
			\item{Graduated \emph{summa cum laude}, with Highest Honors in Mathematics.}
			\item{Computed difficult counterexample in complex analysis with Valentin Matache under Kerrigan Research Minigrants Program.}
			\item{Research on Hopf--Galois theory with Griff Elder under the FUSE grant.}
			\item{Research in Nonlinear Functional Analysis with Anthony Weston at Cornell's Summer Mathematics Institute.}
		\end{cvitems}
	}
	
\end{cventries}





\cvsection{Publications}
\begin{cvparagraph}

Casey Kelleher, Daniel Miller, Trenton Osborn, and Anthony Weston. Strongly non-embeddable metric spaces. \emph{Topology Appl.}, 159(3):749--755, 2012. 

Casey Kelleher, Daniel Miller, Trenton Osborn, and Anthony Weston. Polygonal equalities and virtual degeneracy in \emph{L\textsubscript{p}}-spaces. \emph{J. Math. Anal. Appl.}, 415(1):247--268, 2014. 
\end{cvparagraph}





\cvsection{Work experience}

\begin{cventries}

\cventry
	{Cornell University}
	{Teaching Assistant}
	{Ithaca, NY}
	{August 2012--PRESENT}
	{
		\begin{cvitems}
			\item{Czar's Assistant for Calculus I and II.}
			\item{Teaching assistant for Honors Calculus II and Multivariable Calculus.}
			\item{Grader for Graduate Algebra I and II.}
		\end{cvitems}
	}

\cventry
	{Chesterton House}
	{Resident Advisor}
	{Ithaca, NY}
	{August 2013--May 2014}
	{
		\begin{cvitems}
			\item{Coordinated living responsibilities and events for a household of 15 men.}
		\end{cvitems}
	}

\cventry
	{University of Nebraska Omaha}
	{Tutor at the Math--Science Learning Center}
	{Omaha, NE}
	{January 2012--May 2012}
	{
		\begin{cvitems}
			\item{Tutored undergraduate students in calculus, discrete math, and differential equations.}
		\end{cvitems}
	}
	
\end{cventries}





\cvsection{Coursework and skills}
\begin{cvparagraph}

\textbf{Coursework:} Algebraic topology --- Cloud computing --- Database management systems --- Data structures --- Functional programming --- Linear algebraic groups --- Object-oriented programming --- Operating systems --- Probability theory --- Real analysis --- Smooth manifolds

\textbf{Programming:} C --- C\# --- Java --- \TeX --- Python
\end{cvparagraph}


\end{document}
